Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM

### 2018-08-14 doc/issre2018/issre2018.tex
Prepared camera ready

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
%\usepackage{cite}
\usepackage[noadjust]{cite}
\renewcommand{\citepunct}{,\penalty\citepunctpenalty\,}
\renewcommand{\citedash}{--}% optionally
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[inline]{enumitem}
\usepackage{tablefootnote}
\usepackage{syntax}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{booktabs} % For formal tables
\usepackage{tikz}
\usetikzlibrary{arrows,shadows,positioning,decorations.pathmorphing}
\usepackage{pgf-umlsd}
\usepackage{tikz-uml}
\usepackage{hyperref}
\usepackage{upquote}
\usepackage{listings}
\usepackage{lsthaskell}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{mdframed}
\usepackage{algorithmic}
\usepackage{longtable}
% \usepackage{subcaption}
% \usepackage{subfig}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = red, %Colour of internal links
  citecolor    = green %Colour of citations
}

@@

\newcommand{\Server}{\emph{Server}\xspace}
\newcommand{\Client}{\emph{Client}\xspace}
\newcommand{\User}{\emph{User}\xspace}
\newcommand{\Validator}{\emph{Validator}\xspace}
\newcommand{\thenBr}{\text{then}}
\newcommand{\elseBr}{\text{else}}
\newcommand{\inFor}{\text{inFor}}
\newcommand{\inWhile}{\text{while}}
\newcommand{\un}[1]{\underline{#1}}
\newcommand{\Random}{\mathbb{R}}
\newcommand{\Genetic}{\mathbb{G}}
\newcommand{\RGenetic}{\mathbb{G}_{10}}
\newcommand{\Confix}{\emph{Confix}\xspace}
\newcommand{\Jalangi}{\emph{Jalangi}\xspace}
\newcommand{\Jedi}{\emph{JEDI}\xspace}

@@

\title{Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\begin{abstract}
The popularity of JavaScript is enormous. Together with HTML and CSS, it is the core technology for modern web development. Because of the dynamic nature and complex interplay with HTML, JS applications are often error-prone and vulnerable. Despite active research efforts to devise intricate static and dynamic analyses to facilitate JS testing, the problem of test data generation for JS code interacting with the DOM has not yet been addressed. In this paper, we present a \textbf{J}avascript \textbf{E}volution-based testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}. In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function in combination with the global DOM state. We conducted an empirical evaluation to study the effectiveness and efficiency of our testing framework. It shows that the \emph{genetic with restart} algorithm, proposed in this paper, is able to achieve complete branch coverage for all experimental subjects, taking on average 19 seconds per branch.
\end{abstract}

\begin{IEEEkeywords}
JavaScript, search-based testing, branch coverage
\end{IEEEkeywords}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
%\usepackage{cite}
\usepackage[noadjust]{cite}
\renewcommand{\citepunct}{,\penalty\citepunctpenalty\,}
\renewcommand{\citedash}{--}% optionally
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[inline]{enumitem}
\usepackage{tablefootnote}
\usepackage{syntax}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{booktabs} % For formal tables
\usepackage{tikz}
\usetikzlibrary{arrows,shadows,positioning,decorations.pathmorphing}
\usepackage{pgf-umlsd}
\usepackage{tikz-uml}
\usepackage[bookmarks=false]{hyperref}
\usepackage{upquote}
\usepackage{listings}
\usepackage{lsthaskell}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{mdframed}
\usepackage{algorithmic}
\usepackage{longtable}
% \usepackage{subcaption}
% \usepackage{subfig}
\usepackage{pgfplots}
\pgfplotsset{compat=newest}
\usepackage[titlenotnumbered, linesnumbered, ruled]{algorithm2e} % language for algorithm description
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = red, %Colour of internal links
  citecolor    = green %Colour of citations
}

@@

\newcommand{\jsID}[1]{\texttt{\small #1}}
\newcommand{\Server}{\emph{Server}\xspace}
\newcommand{\Client}{\emph{Client}\xspace}
\newcommand{\User}{\emph{User}\xspace}
\newcommand{\Validator}{\emph{Validator}\xspace}
\newcommand{\thenBr}{\text{then}}
\newcommand{\elseBr}{\text{else}}
\newcommand{\inFor}{\text{inFor}}
\newcommand{\inWhile}{\text{while}}
\newcommand{\un}[1]{\underline{#1}}
\newcommand{\Random}{\mathbb{R}}
\newcommand{\Genetic}{\mathbb{G}}
\newcommand{\RGenetic}{\mathbb{G}_{10}}
\newcommand{\Confix}{\emph{Confix}\xspace}
\newcommand{\Jalangi}{\emph{Jalangi}\xspace}
\newcommand{\Jedi}{\emph{JEDI}\xspace}

@@

\title{Search-Based Test Data Generation for JavaScript Functions that Interact with the DOM
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\begin{abstract}
The popularity of JavaScript (JS) is enormous. Together with HTML and CSS, it is the core technology for modern web development. Because of the dynamic nature and complex interplay with HTML, JS applications are often error-prone and vulnerable. Despite active research efforts to devise intricate static and dynamic analyses to facilitate JS testing, the problem of test data generation for JS code interacting with the DOM has not yet been addressed. In this paper, we present a \textbf{J}avascript \textbf{E}volutionary testing framework with \textbf{D}OM as an \textbf{I}nput, called \emph{JEDI}. In order to reach a target branch, it applies genetic search for relevant input parameters of the JS function in combination with the global DOM state. We conducted an empirical evaluation to study the effectiveness and efficiency of our testing framework. It shows that the \emph{genetic with restart} algorithm, proposed in this paper, is able to achieve complete branch coverage for all experimental subjects, taking on average 19 seconds per branch.
\end{abstract}

\begin{IEEEkeywords}
JavaScript, DOM, search-based testing, branch coverage, genetic algorithm
\end{IEEEkeywords}

### 2018-08-14 doc/issre2018/related-work.tex
Prepared camera ready

The last two decades have been highly productive for the research in JS testing and analysis~\cite{andreasen2017survey, sun2017analysis, mesbah2015advances}. Discussing the state-of-the-art in JS testing we cluster the works, by the underlying technique, into the following categories: feedback-directed random generation~\cite{heidegger2010contract,heidegger2012jscontest,kristensen2017type}, symbolic~\cite{tanida2014automatic,saxena2010symbolic} and concolic~\cite{sen2013jalangi,amin:ase15} execution, static~\cite{tajs2009,dom2011} and dynamic~\cite{andreasen2017survey} analysis, formal verification~\cite{gardner2008local,lerner2012modeling,gardner2012towards}, search-based generation~\cite{alshraideh2008complete}, and whole web application testing~\cite{alshahwan2011automated,mesbah2012invariant,milani2014leveraging}.

@@

\emph{Jalangi}~\cite{sen2013jalangi} is a JS dynamic analysis framework which can be instantiated for \emph{concolic testing} and \emph{type inconsistency analysis}~\cite{pradel2015typedevil}, but it does not support DOM. \emph{Confix}~\cite{amin:ase15} translates DOM-related statements into XPath expressions, and feeds them to a constraint solver in order to construct a DOM fixture. It can reinforce \Jalangi with the capability of DOM modeling. However, as our evaluation has shown, \Confix cannot resolve hard to cover branches. \emph{SymJS}~\cite{tanida2014automatic} employs symbolic execution for JS unit-test generation but again has no symbolic stubs for the DOM API.

@@

Jensen et al.~\cite{tajs2009} proposed a static analysis framework \emph{TAJS} for JS type inference. Later the analysis was extended to support reasoning about the HTML DOM and browser API~\cite{dom2011}. \emph{TAJS} is able to point to dead code, type violation and references to \emph{undefined} values. A review of dynamic analysis techniques ofr JS can be found in a recently published survey~\cite{andreasen2017survey} by Andreasen et al.

Lerner~\cite{lerner2012modeling} formally models the event behavior in the DOM to establish testing oracles. Gardener et al.~\cite{gardner2012towards} presents a formal verification framework for JS, which can deal with some parts the DOM specification~\cite{gardner2008local}.

Alshraideh~\cite{alshraideh2008complete} is the first work suggesting to use GA for JS test data generation. But the implementation is limited to primitive types such as numbers and strings, and does not report on empirical validation. Moreover, it does not support the generation of arrays and DOM. Recently, SBST has been applied to other dynamic languages such as Ruby~\cite{mairhofer2011search}, Lua~\cite{wibowo2015unit} and Go~\cite{irawan2016test}, but the treatment of DOM still makes our approach unique. \emph{XMLMATE}~\cite{havrikov2014xmlmate} is the only search-based tool we have encountered that can produce \emph{tree-like} structures such as XML. It is built on top of \emph{EvoSuite} with the aim of improving the test coverage of the XML-aware Java programs. To generate a random document, it either relies on an existing XML schema, or generates the document from scratch. Both tools have a similar approach for the mutation and crossover. One distinguishing feature of our approach is the use of program analysis to facilitate DOM generation. Jan et al.~\cite{jan2016automated} suggest to use XML fuzzing for identifying vulnerabilities in web services.

@@

One likely direction for the future extension of \emph{JEDI} is \emph{whole test suite generation}~\cite{fraser2013whole}. Such problems usually incur multi-objective optimization~\cite{lakhotia2007multi,panichella2017lips}, e.g. a trade-off between coverage and test-suite length.

Another direction of future work is re-targeting our tool towards mutation-driven generation of unit tests and oracles~\cite{fraser2012mutation}. That should also help to evaluate fault revealing capability of \emph{JEDI} as the number of killed mutants.

Similar to \cite{baars2011symbolic, galeotti2013improving}, it could be worth to combine search-based generation with concolic (symbolic) execution, e.g. investigate the integration of \Jedi with \Jalangi.

We plan to validate \Jedi on a larger set of examples. Towards this goal, we have to extend our framework with the support of such input types as user-defined classes and high-order functions. The first extension is straightforward since any class can be described as the collection of the types of class fields. To generate functions as inputs we could employ an approach similar to QuickCheck~\cite{koopman2006automatic}.

>>>>

The last two decades have been highly productive for the research in JS testing and analysis as revealed by these recent surveys~\cite{andreasen2017survey, sun2017analysis, mesbah2015advances}.
The JS testing research can be clustered, by the choice of underlying technique, into the following categories: feedback-directed random generation~\cite{heidegger2010contract,heidegger2012jscontest,kristensen2017type}, symbolic~\cite{tanida2014automatic,saxena2010symbolic} and concolic~\cite{sen2013jalangi,amin:ase15} execution, static~\cite{tajs2009,dom2011} and dynamic~\cite{andreasen2017survey} analysis, formal verification~\cite{gardner2008local,lerner2012modeling,gardner2012towards}, search-based generation~\cite{alshraideh2008complete}, and whole web application testing~\cite{alshahwan2011automated,mesbah2012invariant,milani2014leveraging}. Let us discuss each separate group of works.

@@

\emph{Jalangi}~\cite{sen2013jalangi} is a JS dynamic analysis framework which can be instantiated for \emph{concolic testing} and \emph{type inconsistency analysis}~\cite{pradel2015typedevil}, but it does not support DOM. \emph{Confix}~\cite{amin:ase15} translates DOM-related statements into XPath expressions, and feeds them to a constraint solver in order to construct a DOM fixture. It can reinforce \Jalangi with the capability of DOM modeling. However, as our evaluation has shown, \Confix cannot resolve hard to cover branches. \emph{SymJS}~\cite{tanida2014automatic} employs symbolic execution for JS unit testing, but again it has no symbolic stubs for the DOM API.

@@

Jensen et al.~\cite{tajs2009} proposed a static analysis framework \emph{TAJS} for JS type inference. Later the analysis was extended to support reasoning about the DOM and browser API~\cite{dom2011}. \emph{TAJS} is able to point to dead code, type violation and references to \emph{undefined} values. A comprehensive review of JS dynamic analysis techniques can be found in a recently published survey~\cite{andreasen2017survey} by Andreasen et al.

Lerner~\cite{lerner2012modeling} formally models the events behaviors in the DOM to establish testing oracles. Gardener et al.~\cite{gardner2012towards} presents a formal verification framework for JS, which can deal with some parts the DOM specification~\cite{gardner2008local}.

Alshraideh~\cite{alshraideh2008complete} is the first work suggesting to use GA for JS test data generation. But the implementation is limited to primitive types such as numbers and strings (no arrays and DOM), and does not report an empirical validation. Recently, SBST has been applied to other dynamic languages such as Ruby~\cite{mairhofer2011search}, Lua~\cite{wibowo2015unit} and Go~\cite{irawan2016test}, but the treatment of DOM still makes our approach unique. \emph{XMLMATE}~\cite{havrikov2014xmlmate} is the only search-based tool we have encountered that can produce \emph{tree-like} structures. It leverages \emph{EvoSuite} as the search-based engine in order to produce an XML input for the testing of Java programs. For random generation, it either relies on an existing XML schema, or generates the document from scratch. Both tools have a similar approach for the mutation and crossover. One distinguishing feature of our approach is the use of program analysis to facilitate DOM generation. Jan et al.~\cite{jan2016automated} suggest to use XML fuzzing for identifying vulnerabilities in web services.

@@

One likely direction for the future extension of \Jedi is \emph{whole test suite generation}~\cite{fraser2013whole}. Such problems usually incur multi-objective optimization~\cite{lakhotia2007multi,panichella2017lips}, e.g. a trade-off between coverage and test suite length.

Another future direction is the mutation testing\cite{fraser2012mutation}, which should help to evaluate the fault revealing capability of \Jedi.

Search-based testing can be strengthened with concolic execution~\cite{baars2011symbolic, galeotti2013improving}. For example, it worth of investigation how to integrate \Jalangi into \Jedi.

We plan to conduct larger evaluation of \Jedi. Therefore, the framework should be extended to support user-defined objects and high-order functions. The first requirement is straightforward since an object can be described as the collection of fields. To generate functions as inputs we could employ an approach similar to QuickCheck~\cite{koopman2006automatic}.
